\documentclass[11pt,a4paper,sans]{moderncv}

\usepackage{verbatim}

\moderncvstyle{classic}
\moderncvcolor{blue}

\usepackage[utf8]{inputenc}                 
\usepackage[scale=0.8]{geometry}
\newcommand\mybitem[1]{%
    \parbox[t]{3mm}{\textbullet}\parbox[t]{10cm}{#1}\\[1.6mm]}

\name{Subham}{Kumar}
\title{Motilal Nehru National Institute Of Technology }


\mobile{+91-7233019175}                  
\social[linkedin]{shubham7120k}
\social[github]{shubham7120k}
\email{Shubham7120k@gmail.com}                    

\begin{document}
\maketitle

\section{Education}

\cventry{2015--present}{Motilal Nehru National Institute of Technology}{Bachelors of Technology,Information Technology }{CGPA:7,84}{}{}
\cventry{2012--2014}{D.A.V. Public School Koyla Nagar ,Dhanbad}{All India Senior School Certificate Examination (2014) }{percentage:95\%}{}{}
\cventry{2000--2012}{D.A.V. Public School Koyla Nagar ,Dhanbad}{All India Secondary School Examination(2012) }{percentage:87.4\%}{}{}

\section{Area of Interest}
\cvline{}{Data Structure}
\cvline{}{Algorithm}
\cvline{}{Machine Learning}

\section{Technical Strength}
\cvline{Languages}{C, C++(stl),Java}
\cvline{Skills}{Blockchain,Android App development}
\cvline{Technologies}{Android,Linux,Docker, \LaTeX{} ,Git}
\section{Project}
\cventry{Jan 2018--present}{Virtual TestBed for testing networking applications}{Undergraduate Mini Project:}{MNNIT,Allahabad , Supervisor:}{Prof Shashwati Banerjea}{}
 
\cvlistitem{Designed a Test bed on mininet-wifi emulator to test performance of a networking applications on scale.}
\cvlistitem{Used Software defined networking to efficiently handle data flow in the network.}
\cventry{May 2018--present}{Personalized Chat Bot}{}{}{}{}
 \vspace{-1\baselineskip}
\cvlistitem{Implemented a self learning chat bot based on LSTM Recurrent Neural Networks.}
\cvlistitem{Given a users conversation dataset from any social network profile of user the chat bot is capable of imitating the user personality.}
\cvlistitem{The bot can generate similar response as the user for a given text message.}



\cventry{Mar 2017--Dec 2017}{CodeMania}{IIT Allahabad ,Hack in The North}{}{}{}
 \vspace{-2.0\baselineskip}
\cvlistitem{Designed and developed an educational android app for competitive programming during 36 hours hackathon.}
\cvlistitem{The app provided features like contest calendar,problemset,tutorial and user rating on different online judge platform }



\cventry{April 2018--May 2018}{Medic-Go}{Smart India Hackathon}{}{}{}
 \vspace{-2.0\baselineskip}
\cvlistitem{Designed an application for finding similar brand drugs in different part of the country.}
\cvlistitem{Implemented a user review system to ensure high probability of availiabilty of suggested drug.}


\section{Achievements}
\cvline{}{ACM-ICPC 2017 Amritapuri Regional Finalist(Rank 26) TeamName:Kazoku}
\cvline{}{Samsung code the next finalist(2018)}
\cvline{}{Winner Techgig Virtual Campus League(2017) an algorithmic coding contest}
\cvline{}{Smart India Hackathon Finalist}
\cvline{}{1st Runner up in  Revengg a reverse engineering  event at Avishkar-2017}
\section{Extra Curricular Activities}
\cventry{2017-present}{Coordinator Computer Club }{MNNIT,Allahabad}{}{}{}
\cvlistitem{Set Problems for and organized Programming Contests for students.}
\cvlistitem{Gave lectures on basics of C.}
\end{document}
